Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans

### 2024-02-14 outputs/paper/paper.qmd
fixed table

---
title: "Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans"
author: 
  - Yuanyi (Leo) Liu
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-s-Impact-on-Young-Americans-Birth-Rates/tree/main. A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802"
date: today
date-format: long
abstract: "In this study, we explore the impact of the Great Recession on birth rates among young people in the United States, utilizing a comprehensive analysis of demographic and economic data. Our findings reveal a significant decline in birth rates within this group during and following the economic downturn, highlighting the intricate relationship between economic stability and reproductive decisions. This research contributes to our understanding of how macroeconomic factors can have profound effects on personal life choices, emphasizing the need for supportive policies targeting young individuals during economic crises."
format: html
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans"
author: 
  - Yuanyi (Leo) Liu
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-s-Impact-on-Young-Americans-Birth-Rates/tree/main. A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802"
date: today
date-format: long
abstract: "In this study, we explore the impact of the Great Recession on birth rates among young people in the United States, utilizing a comprehensive analysis of demographic and economic data. Our findings reveal a significant decline in birth rates within this group during and following the economic downturn, highlighting the intricate relationship between economic stability and reproductive decisions. This research contributes to our understanding of how macroeconomic factors can have profound effects on personal life choices, emphasizing the need for supportive policies targeting young individuals during economic crises."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
